A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-10-01 manuscript.Rmd
strike sentence thatrefers to old figure
fix another code comment refix #66

Figure \@ref(fig:schematic) gives an overview of how the four components of our workflow interact to ensure computational reproducibility. Before we describe the four components in more detail, we begin with a minimal description of the roles of each component. In the remainder of this tutorial, we will further detail each of the four components of our workflow. The first component is version control. Version control manages changes to files (e.g., data and code) over time so that you can recall specific versions of files later or revert the entire project to a past state. Version control offers snapshots of your workflow at different time points identified by a unique identifier. The different frames in the z-axis of Figure  \@ref(fig:schematic) illustrate the different versions of the project. How different parts of a analysis and a report of it relate and in what order they need to be executed is documented using dependency management. The arrows visualize dependencies, such as an analysis depending on the availability of a particular data file. Third, all computer code (such as a statistical analyses in R) is executed in a virtual environment that guarantees exact reproduction of results independent of the host operating system, the locally installed R version, and installed package versions. Finally, dynamic document generation (also known as the literate programming paradigm) interweaves human-readable code and computed results (such as point estimates, p values, or confidence intervals) to eliminate inconsistency errors such as those arising from copy\&paste errors.

@@

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/reproducible-research.git
# (2) obtain a local copy of the remote repository
cd reproducible-research
# (3) run the analysis/data preparation etc. with the local R installation
make all
```

>>>>

Figure \@ref(fig:schematic) gives an overview of how the four components of our workflow interact to ensure computational reproducibility. Before we describe the four components in more detail, we begin with a minimal description of the roles of each component. In the remainder of this tutorial, we will further detail each of the four components of our workflow. The first component is version control. Version control manages changes to files (e.g., data and code) over time so that you can recall specific versions of files later or revert the entire project to a past state. Version control offers snapshots of your workflow at different time points identified by a unique identifier. How different parts of a analysis and a report of it relate and in what order they need to be executed is documented using dependency management. The arrows visualize dependencies, such as an analysis depending on the availability of a particular data file. Third, all computer code (such as a statistical analyses in R) is executed in a virtual environment that guarantees exact reproduction of results independent of the host operating system, the locally installed R version, and installed package versions. Finally, dynamic document generation (also known as the literate programming paradigm) interweaves human-readable code and computed results (such as point estimates, p values, or confidence intervals) to eliminate inconsistency errors such as those arising from copy\&paste errors.

@@

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/reproducible-research.git
# (2) enter the directory containing the project
cd reproducible-research
# (3) run the analysis/data preparation etc. with the local R installation
make all
```
